\thetitle

### 2025-06-26 workshop/examples.tex
replace PT appendix with nutshell section
finish

\section{Examples}
In this section we present a set of minimal examples 
that demonstrate how to use Pigeons.jl for sampling. 
We also direct readers to our growing list of examples at InferHub 
(\url{https://julia-tempering.github.io/InferHub/}), which hosts a  collection of posterior 
distributions with an emphasis on difficult (non-log-concave) problems.

@@

    \item \texttt{min($\alpha$)} and \texttt{mean($\alpha$)}: minimum and average swap 
    acceptance rates during the communication phase across the PT chains.
    See \cref{sec:PT} for a description of PT communication.
\end{itemize}

>>>>

\section{Examples}\label{app:examples}
In this section we present a set of minimal examples 
that demonstrate how to use Pigeons.jl for sampling. 
We also direct readers to our growing list of examples at InferHub 
(\url{https://julia-tempering.github.io/InferHub/}), which hosts a  collection of posterior 
distributions with an emphasis on difficult (non-log-concave) problems.

@@

    \item \texttt{min($\alpha$)} and \texttt{mean($\alpha$)}: minimum and average swap 
    acceptance rates during the communication phase across the PT chains.
\end{itemize}

### 2025-06-26 workshop/overview.tex
finish

>>>>

There are two fundamental concepts in the implementation that we will use
in the following sections. For a distribution $\pi_i$ in the path, we call its
index the $i$-th \emph{chain}. During execution, we assign \emph{replicas} to 
work on the distributions associated to the chains. The map between chains and
replicas is one-to-one, and thus can be seen as a permutation of the 
set $\{1,\dots,N\}$. Replicas are the fundamental unit of parallelization in PT:
they may be distributed across threads, processes, and machines.

In \cref{app:examples} we provide examples of how to use Pigeons.jl. For more details
on the implementation, see \citet{surjanovic2025pigeons}.
